### 2019-02-25 manuscript/results.tex
more editing in Results (diploidization)

% E note to self: keep editing from here XXX

@@

For the two models that only consider diploid and polyploid state (D/P and D/P+A/B) the effect of removing parameter $\delta$ was that net diversification rate of polyploids can be negative with high probability (\cref{figure:netdivnodip}AB).
However, in the models that simultaneously considered polyploidy and breeding system, removing the $\delta$ parameter did not have much of an effect on the location of the posterior distribution of polyploid net diversification rate but on the credible interval width and overlap with net diversification of diploids.
When diploidization was absent, the net diversification of polyploids overlaps with the net diversification of self-compatible diploids but not with the one of self-incompatible diploids (\cref{figure:netdivnodip}CD).
For all models, the posterior distribution of diploidization rate is more uncertain than the one of polyploidization rates (see supplementary information figures).

>>>>

@@

We considered models both with or without diploidization in order to explore the effects of this process on the estimates of state-dependent diversification.
For the two models that only include diploid and polyploid states (D/P and D/P+A/B), the net diversification rate of polyploid lineages is likely negative when diploidization (parameter $\delta$) is excluded but positive when $\delta$ is included (\cref{figure:netdivall}A versus \cref{figure:netdivnodip}A).
For the two models that also included breeding system (ID/CD/CP and ID/CD/CP+A/B), the main effect of including diploidization is increasing the uncertainty of the estimate of polyploid net diversification rate (\cref{figure:netdivall}EF versus \cref{figure:netdivnodip}CD).
For all models, there is greater uncertainty in the estimate of diploidization rate than polyploidization rate, as judged by the width of the credibility intervals (see supplementary information figures). % todo: precise figure refs here
% E: Rosana, would this also be a good place to say something about what we learned regarding the meaningfulness of diploidization in these data?
